\documentclass[11pt, oneside]{article} % use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                  % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                 % ... or a4paper or a5paper or ...

\title{Membership Addendum}

\begin{document}
\maketitle

\section{Overview}
This document defines all membership donation levels for Sad Bee, Inc. as defined in the Bylaws.

\section{Membership Classes}
\begin{enumerate}
	\item Full Member
	\begin{enumerate}
		\item Full Members have the right to:
		\begin{enumerate}
			\item a key or other method of entry to the physical workspace;
			\item twenty-four hour access to the physical workspace;
			\item reasonable inspection rights of corporate records;
			\item store a reasonable amount of equipment at the physical workspace.
		\end{enumerate}
		\item Dues shall be \$50 per month.
	\end{enumerate}
	\item Student Member
	\begin{enumerate}
		\item Student Members shall have the rights and responsibilities of Full Members.
		\item Valid school credentials must be verified by a Director or Officer.
		\item Dues shall be \$13.37 per month.
	\end{enumerate}
	\item Cornerstone Member
	\begin{enumerate}
		\item Cornerstone members shall have all rights and responsibilities of Full Members.
		\item Dues shall be \$100 per month.
	\end{enumerate}
	\item Starving Hacker Member
	\begin{enumerate}
		\item Starving Hacker Members shall have the rights and responsibilities of Full Members.
		\item Starving Hacker Membership must be requested by the Member and approved by both the \textbf{COO} and the \textbf{Board of Directors}.
		\item Starving Hacker Members are expected to volunteer a minimum of \textbf{ten (10) hours} per calendar month towards \textbf{Sad Bee, Inc.} under the supervision of the \textbf{COO}.
		\item Starving Hacker Membership may be revoked at any time by the \textbf{Board of Directors} or the \textbf{COO}.  At this time, the Member must resume paying Full Member dues.
		\item No more than \textbf{ten per cent (10\%)} of the Membership may be this tier; however, no current Starving Hacker Member may be forced out of this tier due to this restriction.
		\item The \textbf{Board of Directors} may approve any rule, regulation, or policy needed to manage this Membership tier.
		\item Dues shall be \$25 per month.
	\end{enumerate}
\end{enumerate}
\end{document}
